\documentclass[12 pt]{exam}
\usepackage[margin=0.75in]{geometry}
\usepackage{amsmath,amssymb,color,amsthm, framed}
\usepackage{enumerate,graphicx,multicol}
\usepackage{wrapfig}
\usepackage{pgf,tikz, subcaption}
\usetikzlibrary{arrows}

\newtheorem{claim}{Claim}
\newtheorem{definition}{Definition}
\newcommand{\soln}[1]{\begin{framed}#1\end{framed} \par}
\printanswers

\pagestyle{head}                       % This causes the exam to only have headers, no footers.
%\runningheadrule                     % This causes the headings to have an underline.

%\firstpageheader{Name:\enspace\hbox to 4.5in{\hrulefill} Section:\enspace\hbox to 1.2in{\hrulefill}}{}{}
%\extraheadheight{.25in}

\begin{document}
\hrule
\begin{center}
  \huge{Math 2710 Problem Set 5: \textsection 4.1-5}    %Title
\end{center}
\hrule
\vskip .2in



\begin{questions}
\question Give a direct proof of  the following statement. If $a$ is an odd integer, then $a+1$ is even.
\begin{solution}\\
Let $a$ be an odd integer. Then $a = 2k + 1$, where $k \in \mathbb{Z}$.
Then $a + 1 = 2k + 1 + 1 = 2k + 2 = 2(k+1)$. Let $n = k + 1$.
Then $a+1 = 2n$, where $n \in \mathbb{Z}$, so $a+1$ is even.
\end{solution}


\question Given component statements $P, Q, R, S,$ and $T$, describe the steps that would
need to be used to prove the compound statement $P \wedge Q \implies \sim (R \vee S) \wedge T$
using the method of direct proof.
\begin{solution}\\
Assume $P$ is true and $Q$ is true. Then, show that $R \lor S$ is false, ie show that $R$ is false
and show that $S$ is false. Finally, show that $T$ is true.
\end{solution}


\question Prove the following. 
Prove that if two integers have the same parity their sum and difference is even.
\begin{solution}\\
Let $x, y \in Z$. If $x$ and $y$ have the same parity, then either $x$ and $y$ are both even,
or $x$ and $y$ are both odd.

If $x$ and $y$ are both even, then $x = 2n$ and $y = 2m$, where $n,m \in \mathbb{Z}$.
Then $x + y = 2n + 2m = 2 (n + m)$. Since $n + m \in \mathbb{Z}$, then $x + y$ is even.
Furthermore, $x - y = 2n - 2m = 2(n-m)$. Since $n-m \in \mathbb{Z}$, then $x-y$ is even.

If $x$ and $y$ are both odd, then $x = 2n+1$ and $y = 2m+1$, where $n,m \in \mathbb{Z}$.
Then $x + y = 2n+1 + 2m+1 = 2 (n+m+1)$. Since $n + m + 1 \in \mathbb{Z}$, then $x + y$ is even.
Furthermore, $x - y = 2n -1 - 2m - 1 = 2(n-m-1)$. Since $n-m-1 \in \mathbb{Z}$, then $x-y$ is even.

Since in both cases the sum and difference is even, we conclude that the sum and difference
of the integers with the same parity is even.
\end{solution}

\question Give a direct proof (or proof by cases) of  the following statement.
For two real numbers $a$ and $b$, $|ab|=|a||b|$.  You may use the following definition:
\begin{definition}
The function $|x|$ is defined as $$\begin{cases} x & x \geq 0 \\ -x & x<0 \end{cases}$$
\end{definition}
\begin{solution}\\
To show that $|ab| = |a||b|$, we consider the following cases:

If $a \ge 0$ and $b \ge 0$, then $|a| = a$, $|b| = b$, and $ab \ge 0$, so $|ab| = ab = |a||b|$.

Now we consider the case where $a < 0$ or $b < 0$, but not both.
Without loss of generality, assume $a \ge 0$ and $b < 0$.
Then $|a| = a$, $|b| = -b$, and $ab < 0$, so $|ab| = -ab = a(-b) = |a||b|$.

If $a < 0$ and $b < 0$, then $|a| = -a$, $|b| = -b$, $ab > 0$, so $|ab| = ab = (-a)(-b) = |a||b|$.

In every case, $|ab| = |a||b|$. \qed
\end{solution}



\newpage
\section*{Extra Problems}


\question State the result proven below, and determine the proof method used.
\begin{proof}
Suppose that $S \subseteq B$ for every $S$ in $\mathcal{S}$, and let $x \in \displaystyle{ \bigcap_{S \in \mathcal{S}}S}$. Then by definition of $\displaystyle{ \bigcap_{S \in \mathcal{S}}S}$, $x$ is an element of some set $T$ in $\mathcal{S}$.

\hspace{.4in} Now, since $S \subseteq B$ for every $S$ in $\mathcal{S}$, it must be true that $T \subseteq B$, and therefore, $x$ is an element of $B$ by definition of $T \subseteq B$. Thus, every element of $\displaystyle{ \bigcap_{S \in \mathcal{S}}S}$ is also an element of $B$.
\end{proof}
\begin{solution}\\
Result: If $S \subseteq B$ for every $S \in \mathcal{S}$, then $\bigcap_{S \in \mathcal{S}} S \subseteq B$.

Proof method: Direct proof.
\end{solution}
	
\question Review the following proof. Determine the proof method used (or attempted) and give the proof a grade of A (complete, correct, and clear), C (partially correct, partially incomplete, and/or partially unclear), or F (not clear, not correct, or not complete). If you give a grade lower than A, explain your reasoning and describe a way to revise the proof for an A.
	\begin{claim}
		Given a positive real number $x$, the sum of $x$ and its reciprocal is greater than $2$.
	\end{claim}
	\begin{proof}
		We seek to prove that if $x \geq 0$, then $x + \dfrac{1}{x} >2$. If we multiply this inequality by $x$, we get the equivalent inequality $x^2 + 1 \geq 2x$. Subtracting $2x$ from both sides, we see that $x^2 - 2x +1 \geq 0$, or in other words $(x-1)^2 \geq 0$. This is true because any real number's square is always positive or zero. So $x + \dfrac{1}{x} >2$ is true.
	\end{proof}


	

\end{questions}

\end{document}
