\documentclass[12 pt]{exam}
\usepackage[margin=0.75in]{geometry}
\usepackage{amsmath,amssymb, amsthm, color}
\usepackage{enumerate,graphicx,multicol}
\usepackage{wrapfig}
\usepackage{pgf,tikz, subcaption}
\usetikzlibrary{arrows}

\noprintanswers
\newtheorem{definition}{Definition}



\pagestyle{head}                       % This causes the exam to only have headers, no footers.
%\runningheadrule                     % This causes the headings to have an underline.

%\firstpageheader{Name:\enspace\hbox to 4.5in{\hrulefill} Section:\enspace\hbox to 1.2in{\hrulefill}}{}{}
%\extraheadheight{.25in}

\begin{document}
\hrule
\begin{center}
  \huge{Math 2710 Problem Set 1: \textsection 1.1-1.4}    %Title
\end{center}
\hrule
\vskip .2in


\begin{questions}

\question For each of the following sets, (i) write the set in set builder notation, i.e. $\left\{x : p(x) \right\}$. Then (ii) write the set as a list of its elements, if possible:
	\begin{parts}
		\part The set of natural numbers whose square is less than 25

		(i) $\{n : n^2 < 25, n \in \mathbb{N}\}$

		(ii) $\{1, 2, 3, 4\}$

		\part $(-1,8]$

		(i) $\{x : -1 < x \le 8, x \in \mathbb{R}\}$

		\part The set of rational numbers less than 4

		(i) $\{r : r < 4, r \in \mathbb{Q}\}$
	\end{parts}
 
\question Determine whether each of the following is true or false. Explain your reasoning for each answer:
	\begin{parts}
		\part The empty set is a proper subset of every set.

		False, $\emptyset$ is not a proper subset of $\emptyset$ because $\emptyset = \emptyset$.

		\part The empty set is an element of every set.

		False, $\emptyset$ is not an element of the set $\{1, 2, 3\}$.

		\part	$\{1\} \in \{1,2,3,\{4\}\}$

		False, the set $\{1\}$ is not an element of $\{1,2,3,\{4\}\}$.

		\part $\{1\} \subseteq \{1,2,3,\{4\}\}$

		True, $\{1\}$ is a subset of $\{1,2,3,\{4\}\}$ because every element of $\{1\}$, i.e. 1, is in $\{1,2,3,\{4\}\}$.

		\part $\{4\} \subseteq \{1,2,3,\{4\}\}$

		False, the set $\{4\}$ is not a subset of $\{1,2,3,\{4\}\}$ because 4 is not in $\{1,2,3,\{4\}\}$.

		\part $\{3\} \subset \mathcal{P}(\mathbb{Q})$

		False, $\{3\}$ is not a proper subset of $\mathcal{P}(\mathbb{Q})$ because 3 is not a subset of $\mathbb{Q}$.

		\part $\{\{\emptyset\}\} \subseteq \mathcal{P}(\{\emptyset, \{\emptyset\}\})$

		True, $\{\{\emptyset\}\}$ is a subset of $\mathcal{P}(\{\emptyset, \{\emptyset\}\}) = \{\emptyset, \{\emptyset\}, \{\emptyset, \{\emptyset\}\}, \{\{\emptyset\}\}\}$
		
	\end{parts}
	
\question Give an example, if possible, of sets $A,B,$ and $C$ satisfying the following. If it is not possible, explain why not.
	\begin{parts}
		\part $A\subseteq B$, $B \subseteq C$, and $C \subseteq A$

		$A = B = C = \{1\}$

		\part $A\subset B$, $B \subset C$, and $C \subset A$

		Impossible because $A\subset B$, $B \subset C$ implies that $|A| < |B| < |C|$, and $C \subset A$ implies $|C| < |A|$. So we have $|A| < |C|$ and $|C| < |A|$, a contradiction.

		\part $A \subseteq B$, $B \nsubseteq C$, and $C \nsubseteq A$

		$A = \{1\}, B = \{1, 2\}, C = \{3\}$

	\end{parts}

\question Write the power set of each of the following sets.
	\begin{parts}
		\part $\{\emptyset, \triangle, \square\}$
		
		$\{\emptyset, \{\emptyset\}, \{\triangle\}, \{\square\}, \{\emptyset, \triangle\}, \{\emptyset, \square\}, \{\triangle, \square\}, \{\emptyset, \triangle, \square\}\}$

		\part $\{a, \{b,\{c\} \} \}$

		$\{\emptyset, \{a\}, \{\{b, \{c\}\}\}, \{a, \{b, \{c\}\}\}\}$
	\end{parts}
	

\question For $A=\{ 1, 2\}$, determine $A \times \mathcal{P}(A)$.

$\mathcal{P}(A) = \{\emptyset, \{1\}, \{2\}, \{1, 2\}\}$

$A \times \mathcal{P}(A) = \{(1, \emptyset), (1, \{1\}), (1, \{2\}), (1, \{1, 2\}), (2, \emptyset), (2, \{1\}), (2, \{2\}), (2, \{1, 2\})\}$

\question Assume $A$ and $B$ are sets with $|A|=4$ and $|B|=3.$ Determine $|A \times B|$. Explain your reasoning. 

$|A \times B| = |A| \times |B| = 12$.

\question Let $$A=\{x | x^2-3x+4=0\} \qquad B=\{x \in\mathbb{Z} | x \textrm{ is divisible by 4} \} \qquad C=\{x \in \mathbb{Z} | x \textrm{ is even}\}.$$  Write out the roster notation of each set, using $\dots$ as needed. Which sets are subsets of each other? 

$A = \emptyset$

$B = \{0, \pm 4, \pm 8, \pm 12, \dots\}$

$C = \{0, \pm 2, \pm 4, \pm 6, \dots\}$

$A \subseteq B, A \subseteq C, B \subseteq C$


\question Let $A=\{1\}, B=\{\{1\},1\}$ and $C=1.$  Using $A$, $B$ and $C$ and the symbols $\subset, \subseteq$ and $\in,$ write as many true statements as possible.

$A \in B$

$A \subset B$

$A \subseteq B$

$C \in A$

$C \in B$

\question We will see the following two definitions later in the course, but you are probably already familiar with them.
\begin{definition} An integer $n$ is \emph{even} if $n=2a$ for some integer $a \in \mathbb{Z}$. \end{definition}
\begin{definition} An integer $n$ is \emph{odd} if $n=2a+1$ for some integer $a \in \mathbb{Z}$. \end{definition}
Read the proofs below. What is being proven? Are there any gaps or holes in the logic?  The first one is well-written while the second is not. What are some things that stand out as bad in the second proof?

\begin{proof} Suppose the integer $x$ is odd. Then $x = 2a+1$ for some $a \in \mathbb{Z}$, by definition
of an odd number. Thus $x^2 = (2a+1)^2 = 4a^2+4a+1 = 2(2a^2+2a)+1$, so
$x^2 = 2b +1$ where $b = 2a^2 +2a \in  \mathbb{Z}$. Therefore $x^2$ is odd, by definition
of an odd number. \end{proof}

\begin{proof} $x = 2k + 1.$
Square it so
\[
x^2 = (2k+1)^2 = 4k^2 + 4k + 1.
\]
That's even, plus one. That's odd. {So it works.}
\end{proof}

The following is being proven: If $x$ is odd, then $x^2$ is odd.

The first proof does not have holes in the logic. The second proof does: the proof does not explicitly say $k \in \mathbb{Z}$ or put $4k^2 + 4k + 1$ into the form $2b + 1$.

The sentences in the second proof are incomplete, it's unclear what "that" refers to, and the proof does not show that $4k^2 + 4k + 1$ can be put into the form $2b + 1, b \in \mathbb{Z}$.

\question Adapt the good proof above (in problem 9) to prove a complimentary statement about even numbers.

Show that if $x$ is even, then $x^2$ is even.

\begin{proof} Suppose the integer $x$ is even. Then $x = 2a$ for some $a \in \mathbb{Z}$, by definition of an even number. Thus $x^2 = (2a)^2 = 4a^2$, so $x^2 = 2b$ where $b = 2a^2 \in \mathbb{Z}$. Therefore $x^2$ is even, by definition of an even number. \end{proof}

\end{questions}

\end{document}
