\documentclass[12 pt]{exam}
\usepackage[margin=0.75in]{geometry}
\usepackage{amsmath,amssymb,color,amsthm}
\usepackage{enumerate,graphicx,multicol}
\usepackage{wrapfig}
\usepackage{pgf,tikz, subcaption, hyperref}
\usetikzlibrary{arrows}
\printanswers %bonus points for me
\newtheorem{claim}{Claim}
\newtheorem{lemma}{Lemma}

\pagestyle{head}                       % This causes the exam to only have headers, no footers.
%\runningheadrule                     % This causes the headings to have an underline.

%\firstpageheader{Name:\enspace\hbox to 4.5in{\hrulefill} Section:\enspace\hbox to 1.2in{\hrulefill}}{}{}
%\extraheadheight{.25in}

\begin{document}
\hrule
\begin{center}
  \huge{Math 2710 Problem Set 11: Ch 11}    %Title
\end{center}
\hrule
\vskip .2in


\begin{questions}

\question A relation $R$ is defined on $S=\{0,1,2,3\}$ by $x\, R \, y$ if $x+y=3.$  Is this relation reflexive? symmetric? transitive? Explain your reasoning. 

\begin{solution}\\
Reflexive: No, $(0, 0) \notin R$ since $0 + 0 \ne 3$, so it is not true that $\forall x \in S, xRx$.

Symmetric: Yes. Assume that $xRy$. Then $x + y = 3$, so $y + x = 3$, and $yRx$.

Transitive: No. $0 R 3$ and $3 R 0$ but it is not true that $0 R 0$ since $0 + 0 \ne 3$.
\end{solution}


\question Give an example of a non-empty relation on the set $A=\{1,2,3\}$ that satisfies the given properties.
In each case, explain your reasoning. 

\begin{parts}
\part symmetric and transitive but not reflexive

\begin{solution}\\
$R = \{(1, 1), (1, 2), (2, 1), (2, 2)\}$

It is symmetric because for all $(x, y) \in R$, $(y, x) \in R$.

It is transitive because if for $x, y, z \in R$, if $xRy$ and $yRz$, then $xRz$.

It is not reflexive because $(3, 3) \notin R$.
\end{solution}


\part reflexive and symmetric but not transitive

\begin{solution}\\
$R = \{(1, 1), (2, 2), (3, 3), (1, 2), (2, 1), (2, 3), (3, 2)\}$

It is reflexive because for all $x \in R$,  $xRx$.

It is symmetric because for all $(x, y) \in R$, $(y, x) \in R$.

It is not transitive because $1R2$ and $2R3$ and $(1, 3) \notin R$.
\end{solution}


\part transitive and reflexive but not symmetric

\begin{solution}\\
$R = \{(1, 1), (2, 2), (3, 3), (1, 2), (2, 3), (1, 3)\}$

It is reflexive because for all $x \in R$, $xRx$.

It is transitive because for all $x, y, z \in R$, if $xRy$ and $yRz$, then $xRz$.

It is not symmetric because $1R2$ and $(2, 1) \notin R$.
\end{solution}


\end{parts}

\question Let $R_1$ and $R_2$ be relations on a set $S$. Prove or disprove the following:
\begin{parts}
\part If $R_1$ and $R_2$ are reflexive, then so is $R_1 \cap R_2$.

\begin{solution}\begin{proof}
Let $s \in S$. Since $R_1$ is reflexive, $(s, s) \in R_1$. Since $R_2$ is reflexive, $(s, s) \in R_2$.

Since $(s, s) \in R_1$ and $(s, s) \in R_2$, then $(s, s) \in R_1 \cap R_2$.

Then $R_1 \cap R_2$ is reflexive since for every $s \in S$, $(s,s) \in R_1 \cap R_2$.
\end{proof}\end{solution}


\part If $R_1$ and $R_2$ are symmetric, then so is $R_1 \cap R_2$. 

\begin{solution}\begin{proof}
Assume that $R_1$ and $R_2$ are symmetric.

Let $(a, b) \in R_1 \cap R_2$. Then $(a, b) \in R_1$, so $(b, a) \in R_1$, and $(a, b) \in R_2$,
so $(b, a) \in R_2$. 

Since $(b, a) \in R_1$ and $(b, a) \in R_2$, then $(b, a) \in R_1 \cap R_2$.

Thus we have that $R_1 \cap R_2$ is symmetric if $R_1$ and $R_2$ are symmetric.
\end{proof}\end{solution}


\part If $R_1$ and $R_2$ are transitive, then so is $R_1 \cap R_2$.  

\begin{solution}\begin{proof}
Assume that $R_1$ and $R_2$ are transitive.

Let $(a, b), (b, c) \in R_1 \cap R_2$. Then $(a, b), (b, c) \in R_1$, so $(a,c) \in R_1$ by transitivity,
and $(a, b), (b, c) \in R_2$, so $(a, c) \in R_2$ by transitivity. Since $(a, c) \in R_1$ and $(a, c) \in R_2$,
then $(a, c) \in R_1 \cap R_2$.

Since we have showed that $(a, b), (b, c) \in R_1 \cap R_2 \implies (a, c) \in R_1 \cap R_2$,
then we have that $R_1 \cap R_2$ is transitive.
\end{proof}\end{solution}


\end{parts}

\question A relation $R$ is defined on $\mathbb{Z}$ by $a \, R \, b$ if $a \equiv b  \mod 2$ or $a \equiv b  \mod 3$. Is $R$ an equivalence relation on $\mathbb{Z}$? 

\begin{solution}\begin{proof}
To determine if $R$ is an equivalence relation on $\mathbb{Z}$, we need to see if $R$ is
reflexive, symmetric, and transitive.\\

Reflexive:

Let $n \in \mathbb{Z}$. Then $n - n = 0 = 0(2)$, so $2 | n-n$, and $n \equiv n \mod 2$, so $nRn$ and we have that
$R$ is reflexive.\\

Symmetric:

Let $a, b \in \mathbb{Z}$. Assume that $aRb$. Then $a \equiv b \mod 2$, in which case $b \equiv a \mod 2$
and $bRa$, or $a \equiv b \mod 3$, in which case $b \equiv a \mod 3$ and also $bRa$. In any case, $bRa$, so
we have that $R$ is symmetric.\\

Transitive:

Let $a = 2$, $b = 4$, $c = 1$. Then $aRb$ since $2 \equiv 4 \mod 2$, and $bRc$ since $4 \equiv 1 \mod 3$.
However, $(a,c) \notin R$ since $2 \not \equiv 1 \mod 2$, and $2 \not \equiv 1 \mod 3$. So $R$ is not transitive.

Then $R$ is \textbf{not} and equivalence relation since it is not transitive.
\end{proof}\end{solution}


\question Review the following proof. Determine the proof method used (or attempted) and give the proof a grade of A (complete, correct, and clear), C (partially correct, partially incomplete, and/or partially unclear), or F (not clear, not correct, or not complete). If you give a grade lower than A, explain your reasoning and describe a way to revise the proof for an A, if possible.

\begin{claim} Every relation which is symmetric and transitive is reflexive. \end{claim}

\begin{proof}
Assume $R$ is a relation on a set $A$ which is symmetric and transitive. We want to show $\forall a \in A, (a \, R \,a)$.  Assume $a\, R \,b$ for some $b \in A$. Then since $R$ is symmetric, $b\, R \,a.$  And since $a\, R \,b$ and $b\, R \,a$, and $R$ is transitive, $a\, R \,a.$  Thus, for all $a \in A$, $a\, R \,a$ so $R$ is reflexive.  
\end{proof}

\begin{solution}\\
I would give the proof a C. The proof is wrong because you cannot assume that there exists some $b \in A$ such
that $a R b$. It is true that if such a $b$ exists, then $aRa$. However, there doesn't have to exist such a
$b \in A$.

As a concrete example, consider the relation $R = \{(1, 1), (2, 2), (1, 2), (2, 1)\}$ on the set $A = \{1,2,3\}$.
Despite being symmetric and transitive, it is not reflexive because $(3, 3) \notin R$. There does not exist
a $b$ such that $3Rb$, and that is where the proof breaks down.

Revise the proof by providing a counterexample since the claim is false.
\end{solution}



\question Fill out the addition and multiplication tables below for $\mathbb{Z}_7$


\begin{solution}\\

\begin{tabular} {c|ccccccc}
$+ $&$[0]$&$[1]$&$[2]$&$[3]$&$[4]$&$[5]$&$[6]$ \\
\hline

$[0]$&0&1&2&3&4&5&6\\
$[1]$&1&2&3&4&5&6&0\\
$[2]$&2&3&4&5&6&0&1\\
$[3]$&3&4&5&6&0&1&2\\
$[4]$&4&5&6&0&1&2&3\\
$[5]$&5&6&0&1&2&3&4\\
$[6]$&6&0&1&2&3&4&5\\
\end{tabular}

\begin{tabular} {c|ccccccc}
$\cdot $&$[0]$&$[1]$&$[2]$&$[3]$&$[4]$&$[5]$&$[6]$ \\
\hline

$[0]$&0&0&0&0&0&0&0\\
$[1]$&0&1&2&3&4&5&6\\
$[2]$&0&2&4&6&1&3&5\\
$[3]$&0&3&6&2&5&1&4\\
$[4]$&0&4&1&5&2&6&3\\
$[5]$&0&5&3&1&6&4&2\\
$[6]$&0&6&5&4&3&2&1\\
\end{tabular}

\end{solution}


\section*{Challenge Problems} 
\question Note: we can also define relations between two different sets. A relation from $A$ to $B$ is a subset of $A \times B.$ Let $A$ be a nonempty set and $B \subseteq \mathcal{P}(A)$. Define a relation $R$ from $A$ to $B$ by $x \, R \, Y$ if $x \in Y$. Given an example of two sets $A$ and $B$ that illustrate this. What is $R$ for these two sets?

\begin{solution}\\
Example 1:

Let $A = \{1, 2\}$ and $B = \{\emptyset, \{1\}, \{2\}, \{1, 2\}\}$.

$R = \{(1, \{1\}), (1, \{1, 2\}), (2, \{2\}), (2, \{1, 2\})\}$\\


Example 2:
Let $A = \{1, 2\}$ and $B = \{\{1, 2\}\}$.

$R = \{(1, \{1, 2\}), (2, \{1, 2\})\}$
\end{solution}


\question Let $S$ be the set of all sequences $(s_n)$, i.e. the set of all infinite lists of real numbers. Define $R$ on the set S by $(s_n) \, R \, (t_n)$ if the set $\{i \in \mathbb{N} : s_i\neq t_i \}$ is finite. Show that $R$ is an equivalence relation. 

\begin{solution}\begin{proof}
We show that $R$ is reflexive, symmetric, and transitive.\\

Reflexive:

Let $(s_n) \in S$. Since $s_i = s_i$ for all $i \in \mathbb{N}$, then
$\{i \in \mathbb{N}: s_i \ne s_i\} = \emptyset$ and therefore finite. So $(s_n) R (s_n)$, and R is reflexive.\\

Symmetric:

Let $(s_n), (t_n) \in S$. Assume that $(s_n) R (t_n)$. Then $\{i \in \mathbb{N}: s_i \ne t_i\}$ is finite, so
$\{i \in \mathbb{N}: t_i \ne s_i\}$ is finite, and $(t_n) R (s_n)$. Then we have that R is symmetric.\\

Transitive:

Let $(s_n), (t_n), (u_n) \in S$. Assume that $(s_n) R (t_n)$ and $(t_n) R (u_n)$.
Then $\{i \in \mathbb{N}: s_i \ne t_i\}$ is finite and $\{i \in \mathbb{N}: t_i \ne u_i\}$ is finite.
Then we have that

$$\{i \in \mathbb{N}: s_i \ne u_i\} \subseteq
\{i \in \mathbb{N}: s_i \ne t_i\} \cup \{i \in \mathbb{N}: t_i \ne u_i\}$$

since in the worst case the terms of the sequences $(s_n)$ and $(u_n)$ differ at every $i$ such that
$s_i \ne t_i$ or $t_i \ne u_i$. Since the union of 2 finite sets is finite, then
$\{i \in \mathbb{N}: s_i \ne u_i\}$ is finite, so $(s_n) R (u_n)$ and we have that $R$ is transitive.


\end{proof}\end{solution}


\end{questions}
\end{document}
